---
title: "Presentation"
author: "Jungwoo Lee, Andy Lu, Jay Shi, Erica Zhong"
date: "November 29, 2018"
output:
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r, error=FALSE, warning=FALSE}
library(jsonlite)
library(ggplot2)
library(knitr)
library(RSQLite)
library(stringr)
library(dplyr)
library(ggplot2)
library(RSelenium)
library(magrittr)
library(janeaustenr)
library(tidytext)
library(jsonlite)
library(dbplyr)
library(ggplot2)
library(knitr)
library(RSQLite)
library(stringr)
library(dplyr)
library(wordcloud)
library(RColorBrewer)
library(grid)
library(gridBase)
library(tm)
library(RSQLite)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
"#F0E442", "#0072B2", "#D55E00", "#CC79A7","#6b3447")
theme1 <- theme_bw() +
theme(axis.text = element_text(size = 8, colour = "#6b3447"),
axis.title = element_text(size = 10, colour = "#2f2f63"),
legend.title = element_text(size = 8, colour = "#2f2f63"),
legend.text = element_text(size = 8, colour = "#6b3447"),
title = element_text(size = 12, colour = "#2f2f63"),
axis.ticks = element_line(colour = "#6b3447"),
plot.caption = element_text(size = 8, colour = "#2f2f63"),
plot.subtitle = element_text(size = 10, colour = "#2f2f63"))

```

```{r}
businesses <- read.csv("yelp_academic_dataset_business.csv", header = TRUE)
head(businesses)
nrow(businesses)
ncol(businesses)
att <- head(businesses$attributes)
```

## Key Aspects

- Overview of Dataset
- Introductory plots
- Difference between restaurants and non-restaurants
- Yelp vs. TripAdvisor 
- kNN Model on Attributes

## Overview of Dataset
- yelp_academic_dataset_business
- 188592 rows
- 16 columns

## Central Question
How can we predict Yelp business star ratings based on business attributes?
Is there a way to gain higher ratings through intentional inclusion of attributes?

## Distribution of Ratings s

```{r}
ggplot(businesses, aes(x = stars)) + geom_bar(stat = "count", fill = "chocolate") + 
  ggtitle("Distribution of Aggregate Ratings of Businesses") +
  xlab("Ratings") +
  ylab("Frequency")
```


## Distribution of Businesses Across States
```{r}
top10States <- sort(table(businesses$state), decreasing = TRUE)[1:10]
otherStates <- dim(businesses)[1] - sum(top10States)
top10States['Others'] <- otherStates
barplot(as.vector(top10States), names.arg = attr(top10States, "names"), main = "Number of Businesses Per State/Province", xlab = "State/Province", ylab = "Count", col = cbPalette)
```


## Distribution of Review Counts

```{r}
grid.newpage()
a <- ggplot(businesses) + aes(x = review_count) + geom_bar(fill = "salmon") + 
  ggtitle("Distribution of Review Counts") + 
  xlim(0,100) +
  xlab("Review Counts") + 
  ylab("Frequency")

b <- ggplot(businesses, aes(x=review_count, y=stars)) + geom_point(size = 0.3, alpha = 0.1) + ggtitle("Ratings vs. Review Counts") + 
  xlim(0,300) +
  xlab("Number of Reviews") + 
  ylab("Star Rating")
vpa <- viewport(x = 0.5, y = 0.5, width = 1, height = 1)
vpb <- viewport(x = 0.70, y = 0.6, width = 0.6, height = 0.6)
print(a, vp = vpa)
print(b, vp = vpb)

```

## Average Rating Across Categories

```{r}
BusiData <- as.data.frame(businesses)
Categories = c("Food", "Barbers", "Home Services", "Health", "Shopping", "Restaurants", "Nightlife", "Bars")
Ave_Review = c()

for (index in 1:length(Categories)){
  Category <- filter(BusiData, str_detect(`categories`, Categories[index]))
  CategoryAverage <- sum(Category$stars)/nrow(Category)
  Ave_Review[index] <- CategoryAverage
}

ggplot(data.frame(Categories), aes(x = Categories, y = Ave_Review, fill = Categories) )+ geom_bar(stat="identity") +  ggtitle("Average Rating Across Categories") +xlab("Categories") + ylab("Average Rating") + theme(axis.text.x = element_text(angle = 35, hjust=1))

```

## Comparison Between Restaurants and Non-Restaurants
```{r}
total <- select(businesses, categories, stars)
restaurantsOnly <- filter(total, str_detect(categories, 'Restaurants'))
notRestaurants <- setdiff(total, restaurantsOnly)

rest <- ggplot(notRestaurants) + aes(x = stars) + geom_bar(fill = "#ABCDEF") +
  ggtitle("Distribution of Aggregate Ratings of Non-restaurants") +
  xlab("Ratings") +
  ylab("Frequency")

nonrest <- ggplot(restaurantsOnly) + aes(x = stars) + geom_bar(fill = "#FF6666") +
  ggtitle("Distribution of Aggregate Ratings of Restaurants") +
  xlab("Ratings") +
  ylab("Frequency")
grid.newpage()
vpr <- viewport(x = 0.5, y = 0.75, width = 1, height = 0.5)
vpnr <- viewport(x = 0.5, y = 0.25, width = 1, height = 0.5)
print(rest, vp = vpr)
print(nonrest, vp = vpnr)
```

## Average Rating Across States
```{r}
stateStars <- select(
  mutate(businesses,
         new_state = ifelse(state %in% attr(top10States, "names"),
                            as.character(state),
                            "Others")),
  new_state, stars
  )

avg_stars <- summarise(
  group_by(stateStars, new_state),
  avg_star = mean(stars)
  )

avg_stars$new_state <- factor(avg_stars$new_state,c("AB","AZ","IL","NC","NV","OH","ON","PA","QC","WI","Others"))

ggplot(avg_stars) +
  aes(x = new_state, y = avg_star, fill = new_state) +
  geom_bar(stat = "identity") +
  ggtitle("Average Ratings across States/Provinces") +
  xlab("State/Province") +
  ylab("Average Ratings")
```

## Yelp vs. TripAdvisor
Two Word Clouds

## Model
- kNN Model
- 20 attributes used to predict star rating of a restaurant
- Trained data on 80% of data, tested on 20%
- k = 5 neighbors
# In simple terms, the k nearest neighbours algorithm is an algorithm that works based on a similarity concept. That is, for any new data point to be predicted based on an existing data set, if the majority of “k” neighbours of the new point belong to a particular class, then the new point also belongs to that class.

## Predicting Using All Attributes
- Accuracy = 57.58%.


## Predicting Using Individual Attributes

#Prereq for these plots:
```{r}
library(RSQLite)
library(data.table)
library(stringr)
library(rlang)
library(caret)
library(dplyr)
library(tidyverse)
library(grid)
library(gridBase)
dcon <- dbConnect(SQLite(), dbname = "yelp.db")
res <- dbSendQuery(conn = dcon, "
SELECT * FROM business LIMIT 35000;
")
df <- dbFetch(res, -1)
dbClearResult(res)
```

Function to extract the attributes and prepare a dataframe for model training. 
```{r}
get_training_df <- function(df, orig_cols, attr_cols) {
  # Input:
  # 1) df - raw business dataframe queried using SQL
  # 2) orig_cols - vector of features you want to include in the output dataframe
  #                that are existing column names of the input dataframe
  # 3) attr_cols - vector of features you want to include in the output dataframe
  #                that need to be extracted from the "attributes" column
  #                of the input dataframe
  # Output: a dataframe ready for training
  # Note: 1) rows that do not contain any feature
  #          in the two input vectors will not be included in the output
  #       2) attr_cols only supports boolean features
  
  # initialize result dataframe
  col_names <-  c(orig_cols, attr_cols)
  result <- data.frame()
  
  for (col in col_names) {
    result[1, col] <- NA
  }
  
  empty_row <- copy(result)
  
  row_extract <- function(row) {
    # Input: a single row of the input dataframe
    # Output: a new single row with all the features
    #         that needs to be added to the result dataframe
    new_row <- copy(empty_row)
    #new_row[1, "name"] <- row[1, "name"]
    
    for (col in orig_cols) {
      val <- row[1, col]
      
      # if this entry of the row in input dafaframe is empty string,
      # the business corresponding to this row will not be included
      # in the output dataframe
      new_row[1, col] <- ifelse(length(val) != 0, val, NA)
    }
    
    # extract all True/False
    values <- str_extract(
      row$attributes[1],
      paste0(
        "(?<='?",
        attr_cols,
        "'?(?:\\s)?[:=]\\s\\\"?)(True|False)"
      )
    )
    
    for (index in 1:length(attr_cols)) {
      attr <- attr_cols[index]
      str <- values[index]

      if (is.na(str)) {
        new_row[1, attr] <- NA
      } else if (str == "True") {
        new_row[1, attr] <- 1
      } else if (str == "False") {
        new_row[1, attr] <- 0
      } else {
        new_row[1, attr] <- 0
      }
    }
    return (new_row)
  }
  
  # stacks up all new rows
  for (row in 1:nrow(df)) {
    result <- rbind(result, row_extract(df[row, ]))
  }
  
  # drops all rows that contain NA
  # result <- na.omit(result)
  rownames(result) <- 1:nrow(result)
  return (result)
}
```


The attributes are listed in the character vector below. 
```{r}
orig_cols <-  c("stars")
attr_cols <- c("BusinessAcceptsCreditCards",
               "garage",
               "street", 
               "validated",
               "lot", 
               "valet", 
               "Caters",
               "GoodForKids",
               "dessert",
               "latenight", 
               "lunch", 
               "dinner", 
               "breakfast",
               "brunch", 
               "HasTV", 
               "OutdoorSeating", 
               "RestaurantsGoodForGroups",
               "RestaurantsReservations",
               "RestaurantsTableService", 
               "WheelchairAccessible")
training_df <- get_training_df(df, orig_cols, attr_cols)
# wifi free = 1 // Alcohol none = 1
```

Set up for all models. If a business does not include a star rating, it is removed from the dataset. The predicted value of the star rating, as well as the actual star rating of a business is rounded to the nearest whole number, for simplicity.
```{r}
funct <- function(a) {  
    return(round(a))
}

Train = head(training_df, 0.8 * nrow(training_df))
Test = tail(training_df, 0.2 * nrow(training_df))
Train <- Train[!is.na(Train$stars),]
Test <- Test[!is.na(Test$stars),]
```

## Model with All Attributes
If a business does not include any attribute, it is removed from the dataset.
```{r}
Train_All <- na.omit(Train)
Test_All <- na.omit(Test)
studentModel <- train(stars ~ ., data=Train_All, method = "knn")
studentTestPred <- predict(studentModel, Test_All)
studentTestPred = sapply(studentTestPred, funct)
Actual = sapply(Test_All$stars, funct)

confusionMatrix(factor(studentTestPred, levels = 1:5), 
                factor(Actual, levels = 1:5))$overall['Accuracy']
```
Here, we use all the attributes listed to predict the star rating of a business and get an accuracy of 54.54%. 

## Individual Attributes
If a business does not include the specified attribute we are training on, it is removed from the dataset.
```{r}
attribute <- function(att) {
  Train2 <- Train[!is.na(Train[att]),]
  Test2 <- Test[!is.na(Test[att]),]
  form <- as.formula(paste('stars ~', att))
  studentModel <- train(form, data=Train2, method = "knn")
  studentTestPred <- predict(studentModel, Test2)
  studentTestPred = sapply(studentTestPred, funct)
  Actual = sapply(Test2$stars, funct)
  acc = confusionMatrix(factor(studentTestPred, levels = 1:5), factor(Actual, levels = 1:5))$overall['Accuracy']
  # print(acc)
}

xd <- data.frame()
xd[1, "Attribute"] <- NA
xd[1, "Accuracy"] <- NA
empty_row <- copy(xd)

for (r in attr_cols) {
  new_row <- copy(empty_row)
  num = attribute(r)
  new_row[1, "Attribute"] <- r
  new_row[1, "Accuracy"] <- num
  xd <- rbind(xd, new_row)
}
xd <- na.omit(xd)
```
Now, we use each of the attributes individually to predict the star rating of a business. The attribute with the best accuracy is GoodForKids at 0.6695652. This is better than using all of the attributes together. 

## Combining Attributes
If a business does not include either of the specified attributes we are training on, it is removed from the dataset.
```{r}
Train3 <- Train[!is.na(Train$GoodForKids),]
Test3 <- Test[!is.na(Test$GoodForKids),]

round3 <- function(att) {
  Train4 <- Train3[!is.na(Train3[att]),]
  Test4 <- Test3[!is.na(Test3[att]),]
  form <- as.formula(paste('stars ~ GoodForKids + ', att))
  studentModel <- train(form, data=Train4, method = "knn")
  studentTestPred <- predict(studentModel, Test4)
  studentTestPred = sapply(studentTestPred, funct)
  Actual = sapply(Test4$stars, funct)
  acc = confusionMatrix(factor(studentTestPred, levels = 1:5), factor(Actual, levels = 1:5))$overall['Accuracy']
}
comb = c("WheelchairAccessible", 
         "garage", 
         "street", 
         "validated")
ca <- data.frame()
ca[1, "Attribute"] <- NA
ca[1, "Accuracy"] <- NA
empty_row <- copy(ca)

for (r in comb) {
  new_row <- copy(empty_row)
  num = round3(r)
  new_row[1, "Attribute"] <- r
  new_row[1, "Accuracy"] <- num
  ca <- rbind(ca, new_row)
}
ca <- na.omit(ca)
ca
```
Now, we will try combinations of attributes to see if a certain combination can be used to train a model with a higher accuracy. Here, we obtained the best accuracy of 69.23% using both GoodForKids and street or validated parking. 



##Star Ratings vs a bunch of attributes: 
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = street)) + geom_jitter(aes(colour = stars))
SP <- training_df[!is.na(training_df$stars),]
SP <- SP[!is.na(SP$street),]

zero <- subset(SP, SP$street == 0)  
one <- subset(SP, SP$street == 1)  

grid.newpage()
vp1 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero, mapping = aes( x = street, y = stars)) + ylim(1, 5)
      + xlab("No Street Parking") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp1)

vp2 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one, mapping = aes( x = street, y = stars))+ ylim(1, 5) 
      + xlab("Street Parking") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp2)
```
The boxplot and scatterplot show that the presence of street parking has a correlation with a higher star rating.

## Star Rating vs. Validated Parking
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = validated)) + geom_jitter(aes(colour = stars))
VP <- training_df[!is.na(training_df$stars),]
VP <- VP[!is.na(VP$validated),]

zero_vp <- subset(VP, VP$validated == 0)  
one_vp <- subset(VP, VP$validated == 1)  

grid.newpage()
vp3 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_vp, mapping = aes( x = validated, y = stars)) 
      + xlab("No Validated Parking") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp3)

vp4 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_vp, mapping = aes( x = validated, y = stars))+ ylim(1, 5) 
      + xlab("Validated Parking") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp4)

```

Though there are few businesses with validated parking, the trend does show that businesses with validated parking have higher ratings than those without.


## Star Rating vs. Good For Kids
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = GoodForKids)) + geom_jitter(aes(colour = stars))

GFK <- training_df[!is.na(training_df$stars),]
GFK <- GFK[!is.na(GFK$GoodForKids),]

zero_gfk <- subset(GFK, GFK$GoodForKids == 0)  
one_gfk <- subset(GFK, GFK$GoodForKids == 1)  

grid.newpage()
vp5 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_gfk, mapping = aes( x = GoodForKids, y = stars)) 
      + xlab("Not Good For Kids") 
      + ylab("Star Rating")
      + ylim(1, 5) 
      + geom_boxplot() , vp = vp5)

vp6 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_gfk, mapping = aes( x = GoodForKids, y = stars))
      + xlab("Good For Kids") 
      + ylab("Star Rating") 
      + ylim(1, 5)
      + geom_boxplot(), vp = vp6)

```
From these plots, we see that there is somewhat of a trend between the presence of the attribute and the star rating of a business. This might mean that having higher reviews depend on whether the business has street parking, validated parking, and provides a good environment for kids, but does not necessarily mean that the presence of any of these attributes guarentees a higher star rating. 


##Star Rating vs WheelchairAccessible
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = WheelchairAccessible)) + geom_jitter(aes(colour = stars))
VP <- training_df[!is.na(training_df$stars),]
VP <- VP[!is.na(VP$WheelchairAccessible),]

zero_vp <- subset(VP, VP$WheelchairAccessible == 0)  
one_vp <- subset(VP, VP$WheelchairAccessible == 1)  

grid.newpage()
vp3 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_vp, mapping = aes( x = WheelchairAccessible, y = stars)) + ylim(1,5)
      + xlab("Not Wheelchair Accessible") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp3)

vp4 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_vp, mapping = aes( x = WheelchairAccessible, y = stars))+ ylim(1, 5) 
      + xlab("Wheelchair Accessible") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp4)
```

##Star Rating vs Credit Cards
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = BusinessAcceptsCreditCards)) + geom_jitter(aes(colour = stars))
VP <- training_df[!is.na(training_df$stars),]
VP <- VP[!is.na(VP$BusinessAcceptsCreditCards),]

zero_vp <- subset(VP, VP$BusinessAcceptsCreditCards == 0)  
one_vp <- subset(VP, VP$BusinessAcceptsCreditCards == 1)  

grid.newpage()
vp3 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_vp, mapping = aes( x = BusinessAcceptsCreditCards, y = stars)) + ylim(1,5)
      + xlab("Bussiness Does Not Accept Credit Cards") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp3)

vp4 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_vp, mapping = aes( x = BusinessAcceptsCreditCards, y = stars))+ ylim(1, 5) 
      + xlab("Bussiness Accepts Credit Cards") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp4)

```

##Star Rating vs Outdoor Seating
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = OutdoorSeating)) + geom_jitter(aes(colour = stars))
VP <- training_df[!is.na(training_df$stars),]
VP <- VP[!is.na(VP$OutdoorSeating),]

zero_vp <- subset(VP, VP$OutdoorSeating == 0)  
one_vp <- subset(VP, VP$OutdoorSeating == 1)  

grid.newpage()
vp3 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_vp, mapping = aes( x = OutdoorSeating, y = stars)) + ylim(1,5)
      + xlab("No Outdoor Seating") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp3)

vp4 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_vp, mapping = aes( x = OutdoorSeating, y = stars))+ ylim(1, 5) 
      + xlab("Has Outdoor Seating") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp4)



```

#Star Rating vs Reservation
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = RestaurantsReservations)) + geom_jitter(aes(colour = stars))
VP <- training_df[!is.na(training_df$stars),]
VP <- VP[!is.na(VP$RestaurantsReservations),]

zero_vp <- subset(VP, VP$RestaurantsReservations == 0)  
one_vp <- subset(VP, VP$RestaurantsReservations == 1)  

grid.newpage()
vp3 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_vp, mapping = aes( x = RestaurantsReservations, y = stars)) + ylim(1,5)
      + xlab("Does Not Accept Reservation") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp3)

vp4 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_vp, mapping = aes( x = RestaurantsReservations, y = stars))+ ylim(1, 5) 
      + xlab("Accepts Reservation") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp4)

```

#Star Rating vs Has TV
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = HasTV)) + geom_jitter(aes(colour = stars))
VP <- training_df[!is.na(training_df$stars),]
VP <- VP[!is.na(VP$HasTV),]

zero_vp <- subset(VP, VP$HasTV == 0)  
one_vp <- subset(VP, VP$HasTV == 1)  

grid.newpage()
vp3 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_vp, mapping = aes( x = HasTV, y = stars)) + ylim(1,5)
      + xlab("Does Not Have TV") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp3)

vp4 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_vp, mapping = aes( x = HasTV, y = stars))+ ylim(1, 5) 
      + xlab("Has TV") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp4)

```

#Star Rating vs Valet
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = valet)) + geom_jitter(aes(colour = stars))
VP <- training_df[!is.na(training_df$stars),]
VP <- VP[!is.na(VP$valet),]

zero_vp <- subset(VP, VP$valet == 0)  
one_vp <- subset(VP, VP$valet == 1)  

grid.newpage()
vp3 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_vp, mapping = aes(x = valet, y = stars)) + ylim(1,5)
      + xlab("Does Not Have TV") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp3)

vp4 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_vp, mapping = aes(x = valet, y = stars))+ ylim(1, 5) 
      + xlab("Has TV") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp4)

```

#Star Rating vs Late Night 
```{r}
ggplot(data = training_df, mapping = aes(x = stars, y = latenight)) + geom_jitter(aes(colour = stars))
VP <- training_df[!is.na(training_df$stars),]
VP <- VP[!is.na(VP$latenight),]

zero_vp <- subset(VP, VP$latenight == 0)  
one_vp <- subset(VP, VP$latenight == 1)  

grid.newpage()
vp3 <- viewport(x = 0.25, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = zero_vp, mapping = aes( x = latenight, y = stars)) + ylim(1,5)
      + xlab("No latenight ") 
      + ylab("Star Rating")
      + geom_boxplot() , vp = vp3)

vp4 <- viewport(x = 0.75, y = 0.5, width = 0.5, height = 1)
print(ggplot(data = one_vp, mapping = aes( x = latenight, y = stars))+ ylim(1, 5) 
      + xlab("Latenight") 
      + ylab("Star Rating") 
      + geom_boxplot(), vp = vp4)

```

##Killer Plot
```{r}
library(grid)
library(gridBase)
grid.newpage()
text_color = "white"

vp.1 <- viewport(x = 0, y = 0.5, w = 0.5, h = 0.5,
                just = c("left", "bottom"))

pushViewport(vp.1)

Negative_Attributes1 = c("no parking","","never","time","","people", "","","","staff","back","dislike","terrible","","")

s_x =c(0.9,0.91,0.9,0.91,0.85,0.83,0.81,0.79,0.78,0.77,0.69,0.64,0.6,0.62,0.61)
s_y = c(0.8,0.75,0.7,0.65,0.7,0.69,0.68,0.55,0.5,0.45,0.43,0.42,0.46,0.48,0.53)
grid.rect(gp = gpar(fill = "black"))

for (i in 1:length(Negative_Attributes1)) {
  if (Negative_Attributes1[i] != ""){
    grid.circle(x = s_x[i], y = s_y[i], r = 0.01,gp=gpar(fill = "yellow"))
  }
  
  grid.text(Negative_Attributes1[i], x = s_x[i], y = s_y[i] + 0.02,gp = gpar(fontsize = 8, fontface = "bold",col = text_color))
}

#Scorpio (negative)
grid.lines(x = c(0.9,0.91,0.9,0.91), y = c(0.8,0.75,0.7,0.65), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))
grid.lines(x = c(0.91,0.85,0.83,0.81,0.79,0.78,0.77,0.69,0.64,0.6,0.62,0.61), y = c(0.75,0.7,0.69,0.68,0.55,0.5,0.45,0.43,0.42,0.46,0.48,0.53), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))

Negative_Attributes2 = c("","","poor","","food","","service","","","","Accepts Credit Card","","","","")
#Cetus (negative)

c_x = c(0.5,0.45,0.4,0.42,0.47,0.45,0.52,0.59,0.62,0.55,0.65,0.69,0.75,0.81)
c_y = c(0.4,0.45,0.4,0.35,0.36,0.3,0.27,0.26,0.18,0.12,0.26,0.23,0.12,0.24)

for (i in 1:length(Negative_Attributes2)) {
  if (Negative_Attributes2[i] != ""){
    grid.circle(x = c_x[i], y = c_y[i], r = 0.01,gp=gpar(fill = "yellow"))
  }
  grid.text(Negative_Attributes2[i], x = c_x[i], y = c_y[i] + 0.02, gp = gpar(fontsize = 8, fontface = "bold", col = text_color))
}

grid.lines(x = c(0.5,0.45,0.4,0.42,0.47,0.5), y = c(0.4,0.45,0.4,0.35,0.36,0.4), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))

grid.lines(x = c(0.42, 0.45,0.52,0.59,0.62,0.55),y = c(0.35,0.3,0.27,0.26,0.18,0.12), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))

grid.lines(x= c(0.59,0.65,0.69,0.75,0.81,0.69), y = c(0.26,0.26,0.23,0.12,0.24,0.23),gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))


Positive_Attributes1 = c("service","validated parking","","No credit Card","","","friendly","","", "staff","")

#Perseus (positive)

per_x = c(0.1,0.04,0.03,0.02,0.01,0.01,0.03,0.04,0.1,0.14,0.18) + 0.07
per_y = c(0.8,0.75,0.65,0.55,0.45,0.3,0.2,0.24,0.55,0.45,0.48)

for (i in 1:length(Positive_Attributes1)) {
  if (Positive_Attributes1[i] != ""){
    grid.circle(x = per_x[i], y = per_y[i], r = 0.01,gp=gpar(fill = "yellow"))
  }
  grid.text(Positive_Attributes1[i], x = per_x[i], y = per_y[i] + 0.02,gp = gpar(fontsize = 8, fontface = "bold",col = text_color))
}

grid.lines(x= c(0.1,0.04,0.03,0.02,0.01,0.01,0.03,0.04) + 0.07,y=c(0.8,0.75,0.65,0.55,0.45,0.3,0.2,0.24),gp = gpar(col = rgb(1,1,0,0.5),lwd = 2))

grid.lines(x = c(0.02,0.1,0.14,0.18) + 0.07, y = c(0.55,0.55,0.45,0.48),gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))

#Hercule(positive)
Positive_Attributes2 = c("love","amazing","","valet","","street parking","","","","garage","","","")
h_x = c(0.43,0.38,0.35,0.38,0.40,0.32,0.32,0.31,0.25,0.26,0.27,0.23,0.20)
h_y = c(0.9,0.83,0.76,0.68,0.60,0.50,0.63,0.73,0.74,0.88,0.55,0.62,0.62)

for (i in 1:length(Positive_Attributes2)) {
  if (Positive_Attributes2[i] != ""){
    grid.circle(x = h_x[i], y = h_y[i], r = 0.01,gp=gpar(fill = "yellow"))
  }
  grid.text(Positive_Attributes2[i], x = h_x[i], y = h_y[i] + 0.02,gp = gpar(fontsize = 8, fontface = "bold",col = text_color))
}

grid.lines(x = c(0.43,0.38,0.35,0.38,0.40,0.32), y = c(0.9,0.83,0.76,0.68,0.60,0.50), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))

grid.lines(x = c(0.26,0.25,0.31,0.32,0.27,0.23,0.20), y = c(0.88,0.74,0.73,0.63,0.55,0.62,0.62), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))

grid.lines(x = c(0.31,0.35), y = c(0.73,0.76), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))

grid.lines(x = c(0.32,0.38), y = c(0.63,0.68),gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))

Neutral_Attributes1 = c("HasTV","child-friendly","","reservation","","latenight")

#Lyra (neutral)
l_x = c(0.76,0.8,0.73,0.64,0.58,0.66)
l_y = c(0.9,0.83,0.8,0.8,0.7,0.7)

for (i in 1:length(Neutral_Attributes1)) {
  if (Neutral_Attributes1[i] != ""){
    grid.circle(x = l_x[i], y = l_y[i], r = 0.01,gp=gpar(fill = "yellow"))
  }
  grid.text(Neutral_Attributes1[i], x = l_x[i], y = l_y[i] + 0.02, gp = gpar(fontsize = 8, fontface = "bold",col = text_color))
}

grid.lines(x = c(0.76,0.8,0.73,0.76),y = c(0.9,0.83,0.8,0.9),gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))
grid.lines(x = c(0.64,0.58,0.66,0.73,0.64), y = c(0.8,0.7,0.7,0.8,0.8), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))


#Microscopium (neutral)
Neutral_Attributes2 = c("","staff", "", "Wheelchair Accessible", "","Outdoor Seating")
m_x = c(0.24,0.3,0.35,0.35,0.24)
m_y = c(0.3,0.3,0.25,0.1,0.15)

for (i in 1:length(Neutral_Attributes2)){
  if (Neutral_Attributes2[i] != ""){
    grid.circle(x = m_x[i], y = m_y[i], r = 0.01, gp=gpar(fill = "yellow"))
  }
  grid.text(Neutral_Attributes2[i],x=m_x[i], y=m_y[i] + 0.02 ,gp = gpar(fontsize = 8, fontface = "bold",col = text_color))
}

grid.lines(x = c(0.24,0.3,0.35,0.35,0.24,0.24), y = c(0.3,0.3,0.25,0.1,0.15,0.3), gp = gpar(col = rgb(1,1,0,0.5), lwd = 2))


grid.text("Constellation of Attributes", y = unit(20.5,"lines"), gp=gpar(fontsize=10, col="white", fontface = "italic"))


popViewport()
```









## Conclusion

