---
title: "Presentation"
author: "Jungwoo Lee, Andy Lu, Jay Shi, Erica Zhong"
date: "November 29, 2018"
output:
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r, error=FALSE, warning=FALSE}
library(jsonlite)
library(ggplot2)
library(knitr)
library(RSQLite)
library(stringr)
library(dplyr)
library(ggplot2)
library(RSelenium)
library(magrittr)
library(janeaustenr)
library(tidytext)
library(jsonlite)
library(dbplyr)
library(ggplot2)
library(knitr)
library(RSQLite)
library(stringr)
library(dplyr)
library(wordcloud)
library(RColorBrewer)
library(grid)
library(gridBase)
library(tm)
library(RSQLite)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
"#F0E442", "#0072B2", "#D55E00", "#CC79A7","#6b3447")
theme1 <- theme_bw() +
theme(axis.text = element_text(size = 8, colour = "#6b3447"),
axis.title = element_text(size = 10, colour = "#2f2f63"),
legend.title = element_text(size = 8, colour = "#2f2f63"),
legend.text = element_text(size = 8, colour = "#6b3447"),
title = element_text(size = 12, colour = "#2f2f63"),
axis.ticks = element_line(colour = "#6b3447"),
plot.caption = element_text(size = 8, colour = "#2f2f63"),
plot.subtitle = element_text(size = 10, colour = "#2f2f63"))

```

```{r}
businesses <- read.csv("yelp_academic_dataset_business.csv", header = TRUE)
head(businesses)
nrow(businesses)
ncol(businesses)
att <- head(businesses$attributes)
```

## Key Aspects

- Overview of Dataset
- Introductory plots
- Difference between restaurants and non-restaurants
- Yelp vs. TripAdvisor 
- kNN Model on Attributes

## Overview of Dataset
- yelp_academic_dataset_business
- 188592 rows
- 16 columns

## Central Question
How can we predict Yelp business star ratings based on business attributes?
Is there a way to gain higher ratings through intentional inclusion of attributes?

## Distribution of Ratings s

```{r}
ggplot(businesses, aes(x = stars)) + geom_bar(stat = "count", fill = "chocolate") + 
  ggtitle("Distribution of Aggregate Ratings of Businesses") +
  xlab("Ratings") +
  ylab("Frequency")
```


## Distribution of Businesses Across States
```{r}
top10States <- sort(table(businesses$state), decreasing = TRUE)[1:10]
otherStates <- dim(businesses)[1] - sum(top10States)
top10States['Others'] <- otherStates
barplot(as.vector(top10States), names.arg = attr(top10States, "names"), main = "Number of Businesses Per State/Province", xlab = "State/Province", ylab = "Count", col = cbPalette)
```


## Distribution of Review Counts

```{r}
grid.newpage()
a <- ggplot(businesses) + aes(x = review_count) + geom_bar(fill = "salmon") + 
  ggtitle("Distribution of Review Counts") + 
  xlim(0,100) +
  xlab("Review Counts") + 
  ylab("Frequency")

b <- ggplot(businesses, aes(x=review_count, y=stars)) + geom_point(size = 0.3, alpha = 0.1) + ggtitle("Ratings vs. Review Counts") + 
  xlim(0,300) +
  xlab("Number of Reviews") + 
  ylab("Star Rating")
vpa <- viewport(x = 0.5, y = 0.5, width = 1, height = 1)
vpb <- viewport(x = 0.70, y = 0.6, width = 0.6, height = 0.6)
print(a, vp = vpa)
print(b, vp = vpb)

```

## Average Rating Across Categories

```{r}
BusiData <- as.data.frame(businesses)
Categories = c("Food", "Barbers", "Home Services", "Health", "Shopping", "Restaurants", "Nightlife", "Bars")
Ave_Review = c()

for (index in 1:length(Categories)){
  Category <- filter(BusiData, str_detect(`categories`, Categories[index]))
  CategoryAverage <- sum(Category$stars)/nrow(Category)
  Ave_Review[index] <- CategoryAverage
}

ggplot(data.frame(Categories), aes(x = Categories, y = Ave_Review, fill = Categories) )+ geom_bar(stat="identity") +  ggtitle("Average Rating Across Categories") +xlab("Categories") + ylab("Average Rating") + theme(axis.text.x = element_text(angle = 35, hjust=1))

```

## Comparison Between Restaurants and Non-Restaurants
```{r}
total <- select(businesses, categories, stars)
restaurantsOnly <- filter(total, str_detect(categories, 'Restaurants'))
notRestaurants <- setdiff(total, restaurantsOnly)

rest <- ggplot(notRestaurants) + aes(x = stars) + geom_bar(fill = "#ABCDEF") +
  ggtitle("Distribution of Aggregate Ratings of Non-restaurants") +
  xlab("Ratings") +
  ylab("Frequency")

nonrest <- ggplot(restaurantsOnly) + aes(x = stars) + geom_bar(fill = "#FF6666") +
  ggtitle("Distribution of Aggregate Ratings of Restaurants") +
  xlab("Ratings") +
  ylab("Frequency")
grid.newpage()
vpr <- viewport(x = 0.5, y = 0.75, width = 1, height = 0.5)
vpnr <- viewport(x = 0.5, y = 0.25, width = 1, height = 0.5)
print(rest, vp = vpr)
print(nonrest, vp = vpnr)
```

## Average Rating Across States
```{r}
stateStars <- select(
  mutate(businesses,
         new_state = ifelse(state %in% attr(top10States, "names"),
                            as.character(state),
                            "Others")),
  new_state, stars
  )

avg_stars <- summarise(
  group_by(stateStars, new_state),
  avg_star = mean(stars)
  )

avg_stars$new_state <- factor(avg_stars$new_state,c("AB","AZ","IL","NC","NV","OH","ON","PA","QC","WI","Others"))

ggplot(avg_stars) +
  aes(x = new_state, y = avg_star, fill = new_state) +
  geom_bar(stat = "identity") +
  ggtitle("Average Ratings across States/Provinces") +
  xlab("State/Province") +
  ylab("Average Ratings")
```

## Yelp vs. TripAdvisor
Two Word Clouds

## Model
- kNN Model
- 20 attributes used to predict star rating of a restaurant
- Trained data on 80% of data, tested on 20%
- k = 5 neighbors
# In simple terms, the k nearest neighbours algorithm is an algorithm that works based on a similarity concept. That is, for any new data point to be predicted based on an existing data set, if the majority of “k” neighbours of the new point belong to a particular class, then the new point also belongs to that class.

## Predicting Using All Attributes
- Accuracy = 57.58%.


## Predicting Using Individual Attributes










## Conclusion

